### 2017-04-06 paper/oopsla17-submission/evaluation.tex
rework gallery with explanations

One threat to validity associated with supervised machine learning is
overfitting (\ie learning a model that is too complex with respect to
the data).
%
We mitigate this threat by having separate training and testing datasets
(\autoref{sec:quantitative}) and via cross-validation
(~\autoref{sec:feature-utility})~\cite{FIXME}.

>>>>

One threat to validity associated with supervised machine learning is
overfitting (\ie learning a model that is too complex with respect to
the data).
%
We mitigate this threat by having separate training and testing datasets
(\autoref{sec:quantitative}) and via cross-validation
(\autoref{sec:feature-utility})~\cite{FIXME}.
